### 2019-06-10 doc/chapters/introduction.tex
Added Addition with Zero Property in introduction.tex

\subsection{No Inflation Property}
\label{property_1}
The decision to verify this property was inspired by the bug found in Bitcoin Core in September 2018  \cite{cve201817144} which could allow to spend the same unspent transaction output (UTXO) in a transaction multiple times.
Hence, new coins could be created out of thin air.
Thus, the property, that a non-coinbase transaction cannot generate new coins, is chosen to be verified in this work.

@@

\subsection{Addition with Zero Property}
\label{property_2}

>>>>

\subsection{No Inflation Property}
\label{property_1}
The decision to verify this property was inspired by the bug found in Bitcoin Core in September 2018  \cite{cve201817144} which could allow to spend the same unspent transaction output (UTXO) in a transaction multiple times.
Hence, new coins could be created out of thin air.
Thus, the property, that a non-coinbase transaction cannot generate new coins, is chosen to be verified in this work.
We call it here as the No Inflation Property.

@@

\subsection{Addition with Zero Property}
\label{property_2}
In Bitcoin-S there is a datatype Satoshis representing an amount of bitcoins.
We verify the addition of Satoshis with zero Satoshis.
This operation should result in the same amount of Satoshis.
We call it in the work as the Addition with Zero Property.

Using Stainless, we successfully verify this property.
But the process of the verification with the tool requires many changes in the code, so that Stainless can accept it.
We look at all needed modifications in chapter \ref{chap:verify_add}.
